MLExplain

### 2018-05-24 paper.tex
Continué

Fortunately the web interface is very simple. It is composed of some auxiliary
JavaScript files, the main JavaScript file containing the logic of the
application and the corresponding HTML page.

\begin{figure*}[ht]
  \centering
  \begin{tikzpicture}[nodes = {align = center}]
    \node (focaml) [draw, text width=2cm] {Interpreter and libraries (OCaml)};

@@

>>>>

\begin{figure*}[t]
  \centering
  \begin{tikzpicture}[nodes = {align = center}]
    \node (focaml) [draw, text width=2cm] {Interpreter and libraries (OCaml)};

@@

\subsection{Solutions to compiler limitations}

As stated before, the backend of our interpreter had to be written in
\texttt{fOCaml} to be integrated into the web interface. This limitation forced
to write non-idiomatic OCaml.

Fortunately the web interface is very simple. It is composed of some auxiliary
JavaScript files, the main JavaScript file -- \texttt{navig-driver.js} --
containing the logic of the application and the corresponding HTML page. The
only modified file is \texttt{navig-driver.js}.
